---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# numpack99

The goal of numpack99 is to provide a number of useful numeric calculation functions.
These functions will help you with:

* calculating the **proper divisors** of an integer (function *divisors()*)
* determining whether two numbers are **amicable** (function *friendly_numbers()*)
* determining whether a number is **perfect** (function *perfect_number()*) 
* calculating the factorial of a number (function *factorial_loop()*)

Please refer to the available additional documentation.

Please note that these functions have been written for the purpose of 

## Author

Massimo Noro, mnoro@yahoo.com

## Status of build as read from Travis latest Build

[![Build Status](https://travis-ci.org/mnoro/numpack99.svg?branch=master)](https://travis-ci.org/mnoro/numpack99)

## Installation

You can install numpack99 from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mnoro/numpack99")
```

## Link to the Git Hub Repository

This is the link to the Git Hub repository:

[Git Hub link] https://github.com/mnoro/numpack99

## Link to the Travis site

This is the link to the repository:

[Travis Link] https://travis-ci.org/mnoro/numpack99/builds/341405470#
