---
title: "numpack99 Vignettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{numpack99 vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Vignette on numpack99
```{r echo=FALSE}
source("../R/friendly_numbers.R")
source("../R/factorial_loop.R")
```



**numpack99** offers access to a selection of functions to work with numbers.

In particular the following:
* amicable numbers
* perfect numbers
* proper divisors

# Perfect Numbers

In number theory a *perfect number* is a positive integer number which is also equivalent to the sum of its **proper divisors**.

**Proper divisors** are all the divisors of a positive integer number except the number itself.
For example the proper divisors of **4680** are:
```{r}
divisors(4680)
```
Their sum is:
```{r}
sum(divisors(4680))
```
The function to assess whether a number is perfect is:
```{r}
perfect_number(4680)
```
One way to see the perfect numbers between 1 and 1000 is as follows:
```{r}
x <- 1:1000
x[sapply(x, perfect_number)]
```
# Amicable numbers

Two positive integer numbers A and B are called amicable if the sums of the proper divisors of A is equal to B and the sums of the proper divisors of B is equal to A.

The first ten amicable pairs are: (220, 284), (1184, 1210), (2620, 2924), (5020, 5564), (6232, 6368), (10744, 10856), (12285, 14595), (17296, 18416), (63020, 76084), and (66928, 66992).

The function *friendly_numbers* allows you to test whwther two numbers are amicable or friendly.
```{r}
friendly_numbers(220, 284)
friendly_numbers(17296, 18416)
friendly_numbers(172960, 184160)
```
# Factorial

Additionally the package provides a function to calculate factorials implemented as a loop.

To use it:
```{r}
factorial_loop(10)
```





